\documentclass[11pt, a4paper]{article}

\usepackage{hyperref}
\usepackage{url}
\usepackage{graphicx}
\graphicspath{{./images/}}

\begin{document}
\title{Title}
\author{Lukas Schimpf}
\date{Dat}
\maketitle
\pagebreak

\begin{flushleft}
Content

\section*{Abstract}

\section*{Problem Definition}
\begin{enumerate}
    \item What is level design.
    \item How can it be improved, automated.
    \item What are some criteria that are important for the system (evaluation criteria).
\end{enumerate}

\section*{Background and Literature Review}
\begin{enumerate}
    \item what is level design.
    \item What is procedural generation.
    \item What is Natural language processing.
    \item What are domain specific languages.
    \item How are 3d object represented in video games.
    \item Some content about vectors and matrices and their relation to 3d games.
    \item Minecraft.
\end{enumerate}

\section*{Methodology / Solution}
\begin{enumerate}
    \item How is the project split up conceptually into layers.
    \item Give justification for each layer.
\end{enumerate}

\subsection*{Layer 1}

\subsection*{Layer 2}

\subsection*{Layer 3}

\subsection*{Layer 4}


\section*{Evaluation and Results}
\begin{enumerate}
    \item Case Studies.
    \item Comment on the accuracy.
    \item Performance.
    \item Comment on the limitations of the system.
\end{enumerate}
% TODO FIND EVALUATION CRITERIA

\section*{Future Work}
\begin{enumerate}
    \item Natural language processing.
    \item Performance optimisation.
    \item AI to learn the definition of structures.
\end{enumerate}

\section*{Conclusion}
\begin{enumerate}
    \item What was achieved and to what degree?
    \item What are some shortcomings of the implementation or what further areas remain to be explored?
\end{enumerate}
    
\end{flushleft}
\end{document}